### 2024-05-18 intro.qmd
20240518 - edits
20240518 - update to save only to html and revealjs
20240518 - video titles
20240518 - add video introductions

::: {.content-visible when-format="html"}

![Benjamin Motz on statistics and fantasy football course](images/motzVideo.mp4){width=100%}

>>>>

::: {.content-visible when-format="html:js"}

Here is a video of a Professor Benjamin Motz that describes the value of teaching statistics through the lens of fantasy football:

![Video of Prof. Benjamin Motz discussing statistics and fantasy football course.](images/motzVideo.mp4){width=100%}
